---
title: "Secondary GBM_miRNA"
author: "Anja Hartewig"
date: "18 1 2022"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(gtools)
library(ComplexHeatmap)
library(circlize)
library(openxlsx)

input_dir <- "C:/Users/gcanha/OneDrive - TUNI.fi/Documents/Secondary GBM/microRNAs/"
```

## Loading the DESeq2 result for RNA-seq in, as well as case-wise normalized counts
```{r}
RNA_results <- read.delim("C:/Users/gcanha/OneDrive - TUNI.fi/Documents/Secondary GBM/RNA-seq/astro_DESeq2_padj_included.CSV",
                           header = TRUE, sep = ";")
DE_RNA_results_no_FC <- RNA_results[which(RNA_results[, 7] < 0.05), ]

RNA_counts_case_wise <- read.delim("C:/Users/gcanha/OneDrive - TUNI.fi/Documents/Secondary GBM/RNA-seq/RNA_seq_gene_counts.txt",
                                    header = TRUE, sep = "\t")
```

## Loading DESeq2 result for miRNA and filtered target predictions in 
```{r}
# target predictions
target_predictions <- read.delim(paste0(input_dir, "filtered_predictions_R.csv"),
                                 sep = ";")

## significant miRNAs
sig_miRNAs <- read.delim(paste0(input_dir, "significant_miRNAs_R.csv"),
                         sep = ";")
sig_miRNAs_new <- sig_miRNAs[which(sig_miRNAs$padj < 0.05), ]

## remove some of the miRNAs due to adj. p-val
target_predictions <- target_predictions[which(target_predictions[, 1] %in% sig_miRNAs_new[, 1]), ]
# in total 11669 targets predicted, 7317 unique ones

## get the list of targets for which we do not have expression data
no_expression_data <- setdiff(target_predictions[, 2], RNA_results[, 1])
targets_expr_filtered <- target_predictions[(target_predictions[, 2] %in% RNA_results[, 1]), ]

for (i in 1:length(targets_expr_filtered[, 2])){
  targets_expr_filtered[i, 3:7] <- RNA_results[which(targets_expr_filtered[i, 2] == RNA_results[, 1]), 2:6]
}

miRNA_stats <- targets_expr_filtered
for (i in 1:length(miRNA_stats[, 1])){
  miRNA_stats[i, 2:9] <- sig_miRNAs[which(miRNA_stats[i, 1] == sig_miRNAs[, 1]), 2:9]
}

## combine the mRNA-seq of the targets with the miRNA-stats table
target_predictions_expression <- cbind(miRNA_stats, targets_expr_filtered[, 2:7])
target_predictions_expression_filtered <- cbind(target_predictions_expression[, 1],
                                                target_predictions_expression[, 10])

## cut the table to only show miRNA, miRNA-LFC, raw_median A and raw_median B, target gene, target LFC, target p-value
### NOTE! The p-value for the genes is not adjusted due to some of the genes not having an adjusted p-value in the original Excel-file
target_predictions_stats <- cbind(target_predictions_expression[, 1],
                                  target_predictions_expression[, 3],
                                  target_predictions_expression[, 8:10],
                                  target_predictions_expression[, 12],
                                  target_predictions_expression[, 15])

colnames(target_predictions_stats) <- c("miRNA", "LFC miRNA",
                                        "raw expression primary",
                                        "raw expression secondary",
                                        "target gene", "target LFC",
                                        "target p-value")
```


## Correlation analysis for target expression (normalized counts)
```{r}
## load in the normalized counts for the mRNA and miRNA
normalized_miRNA_counts <- read.delim(paste0(input_dir, "miRNA_normalized_R.csv"),
                                      header = TRUE, sep = ";")
normalized_mRNA_counts <- read.delim(paste0(input_dir, "mRNA_normalized_R.csv"),
                                     header = TRUE, sep = ";")

## filter for significant miRNAs and targets
## formatting rowname as the gene name
miRNAs_normalized <- normalized_miRNA_counts[(normalized_miRNA_counts[, 1] %in% sig_miRNAs_new[, 1]), ]
rownames(miRNAs_normalized) <- miRNAs_normalized[, 1]
miRNAs_normalized <- miRNAs_normalized[, (-1)]

targets_normalized <- normalized_mRNA_counts[(normalized_mRNA_counts[, 1] %in% target_predictions[, 2]), ]
rownames(targets_normalized) <- targets_normalized[, 1]
targets_normalized <- targets_normalized[, (-1)]

## testing out the Pearson correlation, Pearson is the default value when using cor()
cor(as.numeric(miRNAs_normalized[1, ]), as.numeric(targets_normalized[7286, ]))

## writing a function to calculate the pearson correlation for every target
## using normalized counts
## extract the correlation value and the p-value
correlations <- target_predictions_expression_filtered
correlations_normalized <- matrix(ncol = 3, nrow = dim(target_predictions_expression_filtered)[1])
for (i in 1:dim(target_predictions_expression_filtered)[1]){
  correlations_normalized[i, 1] <- cor(as.numeric(miRNAs_normalized[correlations[i, 1], ]), as.numeric(targets_normalized[correlations[i, 2], ]))
  correlations_normalized[i, 2] <- cor.test(as.numeric(miRNAs_normalized[correlations[i, 1], ]), as.numeric(targets_normalized[correlations[i, 2], ]))$p.value
  correlations_normalized[i, 3] <- cor(as.numeric(miRNAs_normalized[correlations[i, 1], ]), as.numeric(targets_normalized[correlations[i, 2], ]), method = "spearman")
}
correlations <- as.data.frame(cbind(correlations, correlations_normalized))
colnames(correlations) <- c("miRNA", "target", "pearson correlation",
                            "pearson correlation p-val",
                            "spearman correlation")
## adjusting p-value does not work well, only 7 targets remain afterwards
## all with positive correlation

## write the full correlation table to file for GRN
write.table(correlations, file = paste0(input_dir, "correlations_full_new.tsv"),
            quote = FALSE, sep = "\t")

## read in to skip a couple of steps
correlations <- read.delim(paste0(input_dir, "correlations_full_new.tsv"), sep = "\t")

correlations_filtered <- correlations[which(as.numeric(correlations[, 4]) < 0.05), ]

## filtering for pearson and spearman correlation > 0.5
negative_correlation <- c()
for (i in 1:dim(correlations_filtered)[1]){
  negative_correlation[i] <- as.numeric(correlations_filtered[i, 3]) < -0.5 && as.numeric(correlations_filtered[i, 5]) < -0.5
}

negative_correlation_table <- correlations_filtered[negative_correlation, ]
## have a closer look at which targets are predicted for more than 3 miRNAs

## filter out to only show negative correlation
write.table(negative_correlation_table, file = paste0(input_dir, "negatively_correlating_targets.txt"),
            quote = FALSE, row.names = FALSE, sep = "\t")

negative_correlation_table <- read.table(paste0(input_dir, "negatively_correlating_targets.txt"),
                                        sep = "\t", header = TRUE)
write.table(unique(negative_correlation_table[, 2]), file = paste0(input_dir, "all_targets_unique.txt"),
            quote = FALSE, row.names = FALSE, col.names = FALSE)

## extracting the foldchanges for all genes predicted to be targets
target_genes <- negative_correlation_table[, 2]
foldchanges <- c()
adj_p_val <- c()
for (i in 1:length(target_genes)) {
  foldchanges[i] <- RNA_results[which(RNA_results[, 1] == target_genes[i]), 3]
  adj_p_val[i] <- RNA_results[which(RNA_results[, 1] == target_genes[i]), 7]
}
target_genes_full <- cbind(negative_correlation_table, foldchanges, adj_p_val)

## check how many of the targets are DE, independent of the LFC
DE_target_genes <- target_genes_full[target_genes_full[, 7] < 0.05, ]
## the minimum LFC for DE targets is 0.87, based on the RNA-seq results
write.table(unique(DE_target_genes),
            file = paste0(input_dir, "all_correlating_DE_target_genes_miRNAs_no_FC.txt"),
            quote = FALSE, row.names = FALSE, col.names = TRUE)

table(DE_target_genes$miRNA)

DE_target_genes <- read.delim(paste0(input_dir, "all_correlating_DE_target_genes_miRNAs_no_FC.txt"),
                              sep = " ")

## make a separate list for those with FC > 1
DE_target_genes_FC_1 <- DE_target_genes[abs(DE_target_genes[, 6]) > 1, ]

## which of them are regulated by more than 1 miRNA
table(DE_target_genes_FC_1[, 2])[table(DE_target_genes_FC_1[, 2]) > 1]

## write the unique gene names to a file for enrichr
write.table(unique(DE_target_genes_FC_1[, 2]),
            file = paste0(input_dir, "all_correlating_DE_target_genes_miRNAs_FC_1.txt"),
            quote = FALSE, row.names = FALSE, col.names = FALSE)

## write the Nr. per miRNA to file for barplot visualisation
write.table(table(DE_target_genes$miRNA), file = paste0(input_dir, "Nr._correlating_DE_miRNAs_cohorts.tsv"),
            quote = FALSE, row.names = FALSE, sep = "\t")
```

## make a target heatmap for the miRNA targets (Fig S3a)
```{r}
## DE_target_genes, get the counts for them
DE_target_gene_counts <- RNA_counts_case_wise[(RNA_counts_case_wise[, 1] %in% DE_target_genes[, 2]), ]

## obtain the LFCs as well
DE_target_LFC <- RNA_results[(RNA_results[, 1] %in% DE_target_genes[, 2]), ]
## make sure the order is the same
DE_target_gene_counts_sorted <- DE_target_gene_counts[order(DE_target_gene_counts[, 1]), ]
DE_target_LFC_sorted <- DE_target_LFC[order(DE_target_LFC[, 1]), ]

sum(DE_target_gene_counts_sorted[, 1] == DE_target_LFC_sorted[, 1])

rownames(DE_target_gene_counts_sorted) <- DE_target_gene_counts_sorted[, 1]
DE_target_gene_counts_sorted <- DE_target_gene_counts_sorted[, -(1)]

colnames(DE_target_gene_counts_sorted) <- c("TG02a", "TG02b", "TG03a", "TG03b",
                                     "TG04a", "TG04b", "TG05a", "TG05b",
                                     "TG01a", "TG01b", "TG06a", "TG06b")

DE_target_gene_counts_sorted_log <- log2((DE_target_gene_counts_sorted + 1))

grade <- as.factor(as.numeric(c(3, 4, 3, 4, 3, 4, 2, 4, 3, 4, 2, 4)))

ha <- HeatmapAnnotation(grade = grade,
                        col = list(grade = c("2" = "#ffae00b2",
                                             "3" = "#775c40b2",
                                             "4" = "#89138dcb")))

heatmap_pal <- colorRamp2(c(-4, 0, 4), c("#3C5488B2", "white", "#E64B35B2"))

## make the rowannotation
## make a separate data.frame containing the information
miRNAs_anno <- unique(DE_target_genes[, 1])

## loop through the miRNAs
miRNA_anno <- as.data.frame(matrix(data = "none", ncol = 14,
                                   nrow = nrow(DE_target_gene_counts_sorted_log)))
colnames(miRNA_anno) <- miRNAs_anno
rownames(miRNA_anno) <- rownames(DE_target_gene_counts_sorted_log)
for (i in seq_along(miRNAs_anno)) {
  miRNA <- miRNAs_anno[i]
  corr_targets <- DE_target_genes[which(DE_target_genes[, 1] == miRNA), ]
  pos_corr_targets <- corr_targets[corr_targets[, 3] > 0, ]
  neg_corr_targets <- corr_targets[corr_targets[, 3] < 0, ]
  if (length(pos_corr_targets) > 0) {
    for (j in seq_along(pos_corr_targets[, 1])) {
    indices <- which(rownames(miRNA_anno) == pos_corr_targets[j, 2])
    miRNA_anno[indices, i] <- "positive"
    }
  }
  if (length(neg_corr_targets) > 0) {
    for (j in seq_along(neg_corr_targets[, 1])) {
    indices <- which(rownames(miRNA_anno) == neg_corr_targets[j, 2])
    miRNA_anno[indices, i] <- "negative"
    }
  }
}

# Define the colors for the annotations as a named vector
annotation_colors <- c("none" = "white", "positive" = "#dd7b7b", "negative" = "#177a176e")
LFC_col <- colorRamp2(c(-3, 0, 3), c("#00b7d7", "#d5d3d3", "#f83479"))

# Create the row annotation
row_annotation <- rowAnnotation(
  target_of_6500_3p = anno_simple(miRNA_anno[, 1], col = annotation_colors),
  target_of_15b_5p = anno_simple(miRNA_anno[, 2], col = annotation_colors),
  target_of_301b_3p = anno_simple(miRNA_anno[, 3], col = annotation_colors),
  target_of_199a_3p = anno_simple(miRNA_anno[, 4], col = annotation_colors),
  target_of_199b_3p = anno_simple(miRNA_anno[, 5], col = annotation_colors),
  target_of_708_5p = anno_simple(miRNA_anno[, 6], col = annotation_colors),
  target_of_7b_3p = anno_simple(miRNA_anno[, 7], col = annotation_colors),
  target_of_4421 = anno_simple(miRNA_anno[, 8], col = annotation_colors),
  target_of_210_3p = anno_simple(miRNA_anno[, 9], col = annotation_colors),
  target_of_383_5p = anno_simple(miRNA_anno[, 10], col = annotation_colors),
  target_of_4717_3p = anno_simple(miRNA_anno[, 11], col = annotation_colors),
  target_of_187_3p = anno_simple(miRNA_anno[, 12], col = annotation_colors),
  target_of_4746_5p = anno_simple(miRNA_anno[, 13], col = annotation_colors),
  target_of_4741 = anno_simple(miRNA_anno[, 14], col = annotation_colors),
  LFC = anno_simple(DE_target_LFC_sorted[, 3], col = LFC_col)
)

annotation_legend_1 <- Legend(
  labels = names(annotation_colors),
  legend_gp = gpar(fill = annotation_colors),
  title = "Correlation"
)

annotation_legend_2 <- Legend(col_fun = LFC_col,
                              title = "LFC",
                              at = c(-3, 0, 3),
                              labels = c("-3", "0", "3"))

DE_target_gene_counts_sorted_log_scaled <- t(scale(t(DE_target_gene_counts_sorted_log)))
## order them alphabetically
ordered_indices <- c(9, 1, 3, 5, 7, 11, 10, 2, 4, 6, 8, 12)
DE_target_gene_counts_sorted_log_scaled <- DE_target_gene_counts_sorted_log_scaled[, ordered_indices]


pdf(file = paste0(input_dir, "Heatmap_DE_miRNA_targets_log2_scaled_pearson_new.pdf"), width = 12, height = 10)
ht <- Heatmap(DE_target_gene_counts_sorted_log_scaled, top_annotation = ha,
        left_annotation = row_annotation,
        name = "z-score", clustering_distance_rows = "pearson",
        column_title = "log2 counts of all DE miRNA targets, scaled",
        col = heatmap_pal, cluster_columns = FALSE,
        row_names_gp = gpar(fontsize = 8), cluster_rows = FALSE)
draw(ht, annotation_legend_side = "right", annotation_legend_list = list(annotation_legend_1, annotation_legend_2))
dev.off()
```

## Visualising the predicted targets 
make scatterplots to determine the influence of outliers
possibly heatmaps (1 heatmap for each miRNA)
Scatterplots to make: CCNA2, CRY2, NTRK2, CBX2, potentially WEE1
```{r}
## scatterplots, one colour for mRNA, one for miRNA
## different pattern for primary or secondary
## filtering the targets for those that are in the 2097 correlations
target_expr_corr_filtered <- targets_normalized[(rownames(targets_normalized) %in% combined_correlation[, 2]), ]

## only considering the negatively correlating targets
target_expr_neg_corr_filtered <- targets_normalized[(rownames(targets_normalized) %in% negative_correlation_only[, 2]), ]

## filtering out the less interesting ones (e.g. open reading frames)
# less_interesting=target_expr_corr_filtered[grep("orf", rownames(target_expr_corr_filtered)),]

## format the data so it can be used as input for ggplot2
df_mRNA <- as.data.frame(cbind(colnames(target_expr_corr_filtered), t(target_expr_corr_filtered)))
df_miRNA <- as.data.frame(cbind(colnames(target_expr_corr_filtered), t(miRNAs_normalized)))

ggplot() +
  geom_point(data = df_mRNA, aes(x = V1, y = as.numeric(MXRA8))) +
  geom_point(data = df_miRNA, aes(x = V1, y = as.numeric(df_miRNA[, 2]))) +
  theme_bw()

## good to fix the xlab and ylab beforehand to make plots more comprehensible
## possible handle the scatterplots in a miR-specific way

## add a label and then colour distinction for secondary GBM
for (i in 1:33){ # 1 iteration for each significant miRNA
  ## pick the targets associated with that miRNA
  targets <- combined_correlation[which(combined_correlation[, 1] == rownames(miRNAs_normalized)[i]), ]
  expression <- as.data.frame(cbind(t(miRNAs_normalized[rownames(miRNAs_normalized)[i], ]),
                                    t(target_expr_corr_filtered[targets[, 2], ])))
  expression$annotation <- c("lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM")
  ## calculating max mRNA counts to set ylim accordingly
  max_val <- max(expression[, 2:(dim(targets)[1])])
  ## setting the filename to the respective miRNA
  file_name <- paste0(input_dir, rownames(miRNAs_normalized)[i],
               ".pdf", sep = "")
  pdf(file = file_name)
  for (j in 1:(dim(targets)[1] - 1)) { # 1 iteration for each target
    print(ggplot(data = expression, aes(x = expression[, 1], y = expression[, (j + 1)])) +
      geom_point(aes(col = annotation)) +
      theme_bw() +
      xlab("miRNA counts") +
      ylab("mRNA counts") +
      ggtitle(paste0("Expression of ", colnames(expression[j + 1]))) +
      ylim(0, max_val) +
      theme(legend.title = element_text(size = 15),
            legend.text = element_text(size = 14),
            axis.title.x = element_text(size = 15),
            axis.title.y = element_text(size = 15),
            axis.text.x  = element_text(size = 12),
            axis.text.y  = element_text(size = 12),
            plot.title = element_text(size = 17)))
  }
      dev.off()
}

## for the negatively correlating targets
no_negatively_correlating_targets <- c("hsa-miR-548ab", "hsa-miR-7702",
                                       "hsa-miR-216a-5p", "hsa-miR-548ba")
miRNAs_normalized_filtered <- miRNAs_normalized[!(rownames(miRNAs_normalized) %in% no_negatively_correlating_targets), ]
# 1 iteration for each significant miRNA with negatively correlating target
for (i in 1:29) {
  ## pick the targets associated with that miRNA
  targets <- negative_correlation_only[which(negative_correlation_only[, 1] == rownames(miRNAs_normalized_filtered)[i]), ]
  expression <- as.data.frame(cbind(t(miRNAs_normalized_filtered[rownames(miRNAs_normalized_filtered)[i], ]),
                                    t(target_expr_corr_filtered[targets[, 2], ])))
  expression$annotation <- c("lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM",
                             "lower-grade tumor", "secondary GBM")
## calculating max mRNA counts to set ylim accordingly
max_val <- max(expression[, 2:(dim(targets)[1])])
## setting the filename to the respective miRNA
file_name <- paste0(input_dir, rownames(miRNAs_normalized_filtered)[i],
                 "_negative_targets.pdf", sep = "")
pdf(file = file_name)
  for (j in 1:(dim(targets)[1] - 1)) { # 1 iteration for each target
    print(ggplot(data = expression, aes(x = expression[, 1],
                                        y = expression[, (j + 1)])) +
      geom_point(aes(col = annotation)) +
      theme_bw() +
      xlab("miRNA counts") +
      ylab("mRNA counts") +
      ggtitle(paste0("Expression of ", colnames(expression[j + 1]))) +
      ylim(0, max_val) +
      theme(legend.title = element_text(size = 15),
            legend.text = element_text(size = 14),
            axis.title.x = element_text(size = 15),
            axis.title.y = element_text(size = 15),
            axis.text.x  = element_text(size = 12),
            axis.text.y  = element_text(size = 12),
            plot.title = element_text(size = 17)))
  }
  dev.off()
}

targets <- combined_correlation[which(combined_correlation[, 1] == "hsa-let-7b-3p"), ]
expression <- as.data.frame(cbind(t(miRNAs_normalized["hsa-let-7b-3p", ]),
                                  t(target_expr_corr_filtered[targets[, 2], ])))
expression$annotation <- c("lower-grade tumor", "secondary GBM",
                           "lower-grade tumor", "secondary GBM",
                           "lower-grade tumor", "secondary GBM",
                           "lower-grade tumor", "secondary GBM",
                           "lower-grade tumor", "secondary GBM",
                           "lower-grade tumor", "secondary GBM")

# plot(as.numeric(miRNAs_normalized[correlations_filtered[4,1],]), as.numeric(target_expr_corr_filtered[correlations_filtered[4,2],]), type="p", col="black", pch=1, xlab="miRNAs", ylab = "mRNAs", xlim=c(0,))

```

## generating heatmaps for each of the miRNAs
```{r}
# read in an object describing the CNA changes for the miRNAs
CNA_changes <- read.table(paste0(input_dir, "CNAs_R.txt"),
                                 sep = "\t", row.names = 1, header = TRUE)
colnames(CNA_changes) <- sig_miRNAs[, 1]

## putting the miRNA counts in a separate heatmap does not work
## alternatively just take the counts as a separate annotation
## second heatmap annotation object to show if the case has a CNA
## high priority miRNAs: hsa-let-7b-3p
## extract targets + their expression (counts from all patients or general LFC?)
let_7b_targets <- combined_correlation[which(combined_correlation[, 1] == "hsa-let-7b-3p"), ]

miR_130b_3p_targets <- combined_correlation[which(combined_correlation[, 1] == "hsa-miR-130b-3p"), ]

## creating the annotations
sample_names <- colnames(target_expr_corr_filtered)

for (i in 1:33) {
  targets <- combined_correlation[which(combined_correlation[, 1] == rownames(miRNAs_normalized)[i]), ]
  expression <- as.data.frame(rbind(miRNAs_normalized[rownames(miRNAs_normalized)[i], ],
                                    target_expr_corr_filtered[targets[, 2], ]))
  expression_log <- log2(expression + 1)
  colnames(expression_log) <- c("1a", "1b", "2a", "2b", "3a", "3b",
                                "4a", "4b", "5a", "5b", "6a", "6b")
  col_fun <- colorRamp2(c(min(expression_log[1, ]), max(expression_log[1, ])), c("#ffff00", "darkgreen"))
  ha <- HeatmapAnnotation(miRNA_count = anno_simple(as.numeric(expression_log[1, ]), col = col_fun, pch = CNA_changes[, rownames(miRNAs_normalized)[i]]))
  # using anno_simple does not automatically generate legends
  # legend needs to be created manually
  filename <- paste0(input_dir, rownames(miRNAs_normalized)[i], "_Heatmap.pdf", sep = "")
  col_fun_2 <- colorRamp2(c(0, max(expression_log[2:dim(expression_log)[1], ])), c("blue", "red"))
  pdf(file = filename)
  draw(Heatmap(expression_log[2:dim(expression_log)[1], ], name = "mRNA",
               cluster_columns = FALSE, top_annotation = ha,
               column_title = paste0("Log2 transformed target expression of ",
               rownames(miRNAs_normalized)[i])))
  draw(Legend(col_fun = col_fun, title = "miRNA"),
              x = unit(1, "npc"), y = unit(1, "npc"),
              just = c("right", "top"))
  dev.off()
}

## excluding the positive correlating genes
## creating the annotations
no_negatively_correlating_targets <- c("hsa-miR-548ab", "hsa-miR-7702",
                                       "hsa-miR-216a-5p", "hsa-miR-548ba")
miRNAs_normalized_filtered <- miRNAs_normalized[!(rownames(miRNAs_normalized) %in% no_negatively_correlating_targets), ]

CNA_changes_negcor <- read.table(paste0(input_dir, "CNAs_negcorr_R.txt"),
                                 sep = "\t", row.names = 1, header = TRUE)
# adding column names as otherwise the "-" is replaced with a "."
colnames(CNA_changes_negcor) <- sig_miRNAs[!(sig_miRNAs[, 1] %in% no_negatively_correlating_targets), 1]

for (i in 1:29){
  targets <- negative_correlation_only[which(negative_correlation_only[, 1] == rownames(miRNAs_normalized_filtered)[i]), ]
  expression <- as.data.frame(rbind(miRNAs_normalized_filtered[rownames(miRNAs_normalized_filtered)[i], ],
                                    target_expr_corr_filtered[targets[, 2], ]))
  expression_log <- log2(expression + 1)
  colnames(expression_log) <- c("1a", "1b", "2a", "2b", "3a", "3b",
                                "4a", "4b", "5a", "5b", "6a", "6b")
  col_fun <- colorRamp2(c(min(expression_log[1, ]), max(expression_log[1, ])), c("yellow", "darkgreen"))
  ha <- HeatmapAnnotation(miRNA_count = anno_simple(as.numeric(expression_log[1, ]), col = col_fun, pch = CNA_changes_negcor[, rownames(miRNAs_normalized_filtered)[i]]))
  # using anno_simple does not automatically generate legends
  # create legend manually
  filename <- paste0(input_dir, rownames(miRNAs_normalized_filtered)[i], "_negcorr_Heatmap.pdf", sep = "")
  col_fun_2 <- colorRamp2(c(0, max(expression_log[2:dim(expression_log)[1], ])), c("blue", "red"))
  pdf(file = filename)
  draw(Heatmap(expression_log[2:dim(expression_log)[1], ], name = "mRNA",
              cluster_columns = FALSE, top_annotation = ha,
              column_title = paste0("Log2 transformed target expression of ",
              rownames(miRNAs_normalized_filtered)[i])))
  draw(Legend(col_fun = col_fun, title = "miRNA"), x = unit(1, "npc"), y = unit(1, "npc"), just = c("right", "top"))
  dev.off()
}
```
